Practicing with the data

### 2017-07-07 practice.Rmd
practice with text mining

#26 observations in out dataframe have negative time to event variable
length(which(out$time_until_answer < 0))
```

@@

>>>>

#26 observations in out dataframe have negative time to event variable
length(which(out$time_until_answer < 0))
library(dplyr)
out %>% 
  filter(time_until_answer < 0) %>%
  select(post_date, first_answer_date, answered)
```

@@

### practicing with text mining
```{r}
library(dplyr)
#working only with the 2000 questions that were answered the fastest
arranged <- out1_positive %>% arrange(time_until_answer)
fastest <- arranged[1:2000,]

library(qdap)
library(tm)
# INSTALLING RWEKA NOT WORKING
# library(RWeka)
# 
# titles <- fastest$title
# 
# #clean titles 
# qdap_clean <- function(x) {
#   x <- replace_abbreviation(x)
#   x <- replace_contraction(x)
#   x <- replace_number(x)
#   x <- replace_ordinal(x)
#   x <- replace_symbol(x)
#   x <- tolower(x)
#   return(x)
# }
# tm_clean <- function(corpus) {
#   tm_clean <- tm_map(corpus, removePunctuation)
#   corpus <- tm_map(corpus, stripWhitespace)
#   corpus <- tm_map(corpus, removeWords, stopwords("en"))
#   return(corpus)
# }
# 
# tokenizer <- function(x) {
#   NGramTokenizer(x, Weka_control(min = 2, max = 3)) }
# 
# titles <- qdap_clean(titles)
# titles_cor <- VCorpus(VectorSource(titles))
# titles_corpus <- tm_clean(titles_cor)
# 
# titles_tdm <- TermDocumentMatrix(titles_corpus, )
```
